Idea Development

### 2025-01-06 ProjectBlog/others/Abortion/abortion.qmd
abortion add

---
title: "Idea Development"
date: 10/29/2024
date-modified: last-modified
draft: true
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
bibliography: references.bib
---

>>>>

---
title: "Idea Development"
date: 10/29/2024
date-modified: last-modified
draft: false
date-format: full
categories: [Others]
website:
  comments: 
    utterances:
      repo: quarto-dev/quarto-web
#image: "cluster1.png"
tbl-colwidths: [5,30,125]
format: 
  html:
    page-layout: full
bibliography: references.bib
---
